---
title: "Probability and Statistics with R, Second Edition"
output: html_document
---

```{r setup, include=FALSE}
library(PASWR2)
knitr::opts_chunk$set(echo = TRUE, comment = NA)
```

## Errata

--------------------

<center> Last Updated on: `r format(Sys.time(), "%b %d, %Y at %X")` </center>

--------------------

* Page 132 Example 2.21 had the following:

```{r}
meanSEC <- mean(SDS4$times)
meanMIN <- mean(SDS4$times/60)
c(meanSEC, meanMIN)
sdSEC <- sd(SDS4$times)
sdMIN <- sd(SDS4$times/60)
c(sdSEC, sdMIN)
CVsec <- meanSEC/sdSEC
CVmin <- meanMIN/sdMIN
c(CVsec, CVmin)
```
 changed to
 
```{r}
meanSEC <- mean(SDS4$times)
meanMIN <- mean(SDS4$times/60)
c(meanSEC, meanMIN)
sdSEC <- sd(SDS4$times)
sdMIN <- sd(SDS4$times/60)
c(sdSEC, sdMIN)
CVsec <- sdSEC/meanSEC
CVmin <- sdMIN/meanMIN
c(CVsec, CVmin)
```

* Page 209: ...conditioning event G, *then* enumerating... should read: conditioning event G, *than* enumerating  

* Page 244: Problem 54 - Given the following cumulative *density* function should read Given the following cumulative *distribution* function

* Page 340: R Code 5.15 - `facet_grid(. ~ r)` should read `facet_grid(. ~ r, labeller = label_parsed)`

* Page 485: `lep <- (15 - 1) + 5.2449/uchi` should be `lep <- (15 - 1) + 5.2429/uchi`, and
`uep <- (15 - 1) + 5.2449/lchi` should be `uep <- (15 - 1) + 5.2429/lchi`

* Page 545: Exampe 9.11 - `STCHOOL` should be `STSCHOOL`

* Page 551: $T=\frac{\bar{D}-\mu_{D}}{S_D/\sqrt{n_D}} \sim t_{n - 1}$ should be $T=\frac{\bar{D}-\mu_{D}}{S_D/\sqrt{n_D}} \sim t_{n_D - 1}$

* With update in `ggplot2`, everywhere `ggplot_hline(y = value)` appears now needs to be `ggplot_hline(yintercept = value)`


 


-------------------

* If you find typos or errors, please report them at [https://github.com/alanarnholt/PASWR2E-Book/issues](https://github.com/alanarnholt/PASWR2E-Book/issues) so we can fix them.

-------------------